Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-09 eswc-2012/phdsymp.tex
delete old text...
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@173 43ef1190-90fd-4dd7-a769-d0121f02b80e
merely anecdotal
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@174 43ef1190-90fd-4dd7-a769-d0121f02b80e

%   Discontent with current state of the art in benchmarking prompts the
%   author to focus on the evaluation problem and to investigate whether
%   we can provide better advices to new users selecting a SPARQL engine
%   to use.
\end{abstract}

@@

% With the currently published benchmarks, it is up to the user to
% select an engine with the best characteristics, relative to their own
% expected application. New users often are unable to formulate
% \emph{any} relevant expectations. For these users, the wide variety of
% benchmarks, for instance by the TPC, offers little help as a thorough
% understanding of the benchmarks and what they measure is required to
% select an engine. To help these users, we should ask ourselves:
% Can we collapse all the metrics into a single \emph{test
%   statistic} that can summarize the performance of the engine as a
% whole? Also, can we provide a system for developers that they can use
% to see if any changes they do to the engine can have unexpected adverse
% effects on other parts of the system? For those who can formulate
% relevant expectations, weighing different parts of the system or
% metrics is more useful and will yield a more tenable answer, and
% motivates the question: Can we use the system to better find the
% distinguishing characteristics so that we can return a question that
% will actually help new users of SPARQL engines to chose one that meets
% their needs?

% The above relies on data and queries that are representative of the
% system as a whole. It is often asserted that it is not possible to
% create a ``one-size-fits-all'' benchmark but answering the above
% question requires such a benchmark. The relative simplicity of RDF and
% SPARQL may make this feasible.

@@

With this analysis, I speculate based on superficial experience with
factorial designs and analysis of variance that certain estimated
coefficients can be exposed in the service description to give
federated query engines assistance in optimizing for performance
characteristics of certain SPARQL implementations. 
%Adjusting how
%different features are weighed will help those who know details of
%their expected SPARQL use and normalization-techniques of the weights
%will answer the special case of ``the best general-purpose SPARQL
%engine''.

>>>>

% TODO Here
\end{abstract}

@@

Furthermore, the current approach presents merely anecdotal evidence
that one engine is better than another with respect to
performance. It may be that while the benchmarking queries do seem to
favor one engine, other queries that have not been tried may reveal
that there are strong adverse effects that may not have been
anticipated. A more systematic approach is needed to provide a
comprehensive and objective basis for comparing SPARQL engines.

% TODO here

@@

With this analysis, I speculate based on superficial experience with
factorial designs and analysis of variance that certain estimated
coefficients can be exposed in the service description to give
federated query engines assistance in optimizing for performance
characteristics of certain SPARQL implementations.

% TODO here
